Copyright

### 2025-03-05 copyright.qmd
Specify knitr as engine for pages
We rely on knitr-specific syntax
throughout the tutorial, even in
instances where no code is executed.

---
title: "Copyright"
format:
  html:
    include-in-header:
      - text: |
          <style>
          .unstyled-list > ul {
              list-style-type: none;
              padding-left: 1rem;
          }
          .unstyled-list summary {
              cursor: pointer;
          }
          </style>
---

>>>>

---
title: "Copyright"
engine: knitr
format:
  html:
    include-in-header:
      - text: |
          <style>
          .unstyled-list > ul {
              list-style-type: none;
              padding-left: 1rem;
          }
          .unstyled-list summary {
              cursor: pointer;
          }
          </style>
---
